The Concurrent Calculi Formalisation Benchmark

### 2023-10-10 paper/paper.tex
Add synctex support
Revise abstract

\documentclass[runningheads]{llncs}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathpartir}
\usepackage{cite}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{hyperref}
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{abstract}
  The POPLMark challenge sparked a flurry of work on machine-checked
  proofs. However, POPLMark (and its follow-up POPLMark Reloaded) were
  purposedly limited in scope, with benchmark problems that do not
  address concurrency. For this reason, we propose a new collection of
  benchmark problems with a focus on the issues encountered when
  mechanising message-passing concurrency using process calculi. Our
  benchmark problems concern linear handling of environments, scope
  extrusion, and coinductive reasoning. Our goal is to clarify,
  compare and advance the state of the art.

>>>>

\documentclass[runningheads]{llncs}
\synctex=1
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathpartir}
\usepackage{cite}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{hyperref}
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{abstract}
  The POPLMark challenge and its follow-up POPLMark Reloaded sparked a flurry of
  work on machine-checked proofs, and forstered the adoption of proof
  mechanisation in programming language research.  However, both POPLMark and
  POPLMark Reloaded were purposely limited in scope, with benchmark problems
  that do not address concurrency-related issues.
  %
  For this reason, we propose a new collection of benchmark problems with a
  focus on the challenges and issues that typically arise when mechanising
  message-passing concurrency using process calculi.  Our benchmark problems
  address three key topics: linearity, scope extrusion, and coinductive
  reasoning.  The goal of this new challenge is to clarify, compare, and advance
  the state of the art, fostering the adoption of proof mechanisation in future
  research on message-passing concurrency.
